An elaborate data set on human gait and the effect of mechanical perturbations

### 2014-12-13 paper.tex
Added image of treadmill and motion capture system, closes #53.
Added IRB #, closes #62.

\section*{Participants}
The study was approved by the Institutional Review Board of Cleveland State University
and informed consent was obtained from all participants.
%
Fifteen able bodied subjects including four females and eleven males with an
average age of $24\pm4$ years, height of $1.75\pm0.09$ m, mass of $74\pm13$ kg
participated in the study. The data has been anonymized with respect to the
participants' identities and a unique identification number was assigned to
each subject. A selection of the meta data collected for each subject is shown
in Table~\ref{tab:subjects}.
%
\begin{table*}
  \cprotect\caption{Information about the 15 participants. The final three
    columns give the trial numbers associated with each nominal treadmill
    speed. Additional trials with subject 0 are trials with no subject, i.e.
    unloaded trials that can be used for inertial compensation purposes, and are
    not shown in the table. Generated by \verb|src/subject_table.py|.}
  \centering
  \input{tables/subjects.tex}
  \label{tab:subjects}
\end{table*}

@@

Our motion capture system's coordinate system is such that the X coordinate
points to the right, the Y coordinate points upwards, and the Z coordinate
follows from the right-hand-rule, i.e. points backwards with respect to a
person walking forward on the treadmill. The camera's coordinate system is
aligned to an origin point on treadmill's surface during camera calibration.
The same point is used as the origin of the ground reaction force measuring
system.

>>>>

\section*{Participants}
%
The study was approved by the Institutional Review Board of Cleveland State
University (\# 29904-VAN-HS) and informed consent was obtained from all
participants.

Fifteen able bodied subjects including four females and eleven males with an
average age of $24\pm4$ years, height of $1.75\pm0.09$ m, mass of $74\pm13$ kg
participated in the study. The data has been anonymized with respect to the
participants' identities and a unique identification number was assigned to
each subject. A selection of the meta data collected for each subject is shown
in Table~\ref{tab:subjects}.
%
\begin{table*}
  \cprotect\caption{Information about the 15 participants. The final three
    columns give the trial numbers associated with each nominal treadmill
    speed. Additional trials with subject 0 are trials with no subject, i.e.
    unloaded trials that can be used for inertial compensation purposes, and are
    not shown in the table. Generated by \verb|src/subject_table.py|.}
  \centering
  \input{tables/subjects.tex}
  \label{tab:subjects}
\end{table*}

@@

Our motion capture system's coordinate system is such that the X coordinate
points to the right, the Y coordinate points upwards, and the Z coordinate
follows from the right-hand-rule, i.e. points backwards with respect to a
person walking forward on the treadmill. The camera's coordinate system is
aligned to an origin point on treadmill's surface during camera calibration.
The same point is used as the origin of the ground reaction force measuring
system. Figure~\ref{fig:treadmill} shows the layout of the equiptment.

\begin{figure*}
  \centering
  \includegraphics{figures/treadmill.png}
  \caption{The treadmill, cameras, projection screen, and saftey rope. The
    direction of travel is in the $-z$ direction.}
  \label{fig:treadmill}
\end{figure*}
